---
title: "Part 2 Feature Building"
output: 
  html_document: 
       smart: false
---

# Libraries

```{r}
library(data.table)
library(dplyr)
```

# Loading the Data

```{r}
order_products_all <- fread('order_products_all.csv')
head(order_products_all)
orders <- fread('orders.csv')
head(orders)
```

Creating a day_part variable to group the hours:
```{r}
orders[,day_part:='Night']
orders[(order_hour_of_day>=7 & order_hour_of_day<=14),day_part:='Morning']
orders[(order_hour_of_day>=15 & order_hour_of_day<=23),day_part:='Evening']
```


Transforming the categorical variables to characters

```{r}
order_products_all <- order_products_all[,user_id:=as.character(user_id)]
orders <- orders[,order_dow:=as.character(order_dow)]
orders <- orders[,order_hour_of_day:=as.character(order_hour_of_day)]
orders <- orders[,user_id:=as.character(user_id)]
orders$user_id <- as.character(orders$user_id)
head(orders)
```




# Feature Building

## A)  Ordering Patters

### 1. Days between orders
This indicates how often and/or loyal a particular customer is to this online retailer

```{r}
# calculate the features
min_days <- orders[,min(days_since_prior_order,na.rm=TRUE),by=user_id]
max_days <- orders[,max(days_since_prior_order,na.rm=TRUE),by=user_id]
med_days <- orders[,median(days_since_prior_order,na.rm=TRUE),by=user_id]

# merge the features
user_days <- merge(min_days,max_days,by='user_id', all=TRUE)
user_days <- merge(user_days,med_days, by='user_id',all=TRUE)
names(user_days)[2:4] <- c('min_days','max_days','med_days')

# delete the original calculations from the workspace
rm(min_days,max_days,med_days)
```

### 2) Day of Week 
The % of Orders for each user_dow combination
```{r}
user_dow <- orders[,length(order_id),by=c('user_id','order_dow')]
names(user_dow)[3] <- "dow_orders"
user_orders <- orders[,length(order_id),by=c('user_id')]
names(user_orders)[2] <- "total_orders"

#calculate the percentage
user_dow <- merge(user_dow,user_orders,by='user_id')
user_dow <- user_dow[,user_dow_percentage:=dow_orders/total_orders]
user_dow$dow_orders <- NULL
user_dow$total_orders <- NULL

# pivot
user_dow <- dcast(user_dow, user_id ~ order_dow, value.var="user_dow_percentage")

#replace NAs with 0
user_dow[is.na(user_dow)] <- 0

```

### 2) Day of Week and Day Part

```{r}
user_dow_day_part <- orders[,length(order_id),by=c('user_id','order_dow','day_part')]
names(user_dow_day_part)[4] <- "dow_day_part_orders"

#calculate the percentage
user_dow_day_part <- merge(user_dow_day_part,user_orders,by='user_id')
user_dow_day_part <- user_dow_day_part[,dow_day_part_percentage:=dow_day_part_orders/total_orders]
user_dow_day_part$dow_day_part_orders <- NULL
user_dow_day_part$total_orders <- NULL

user_dow_day_part$dow_dp <- paste(user_dow_day_part$order_dow,user_dow_day_part$day_part,sep="-")

# pivot
user_dow_day_part <- dcast(user_dow_day_part, user_id ~ dow_dp, value.var="dow_day_part_percentage")

#replace NAs with 0
user_dow_day_part[is.na(user_dow_day_part)] <- 0

```

### 3) Day Part


```{r}
user_dp <- orders[,length(order_id),by=c('user_id','day_part')]
names(user_dp)[3] <- "dp_orders"

#calculate the percentage
user_dp <- merge(user_dp,user_orders,by='user_id')
user_dp <- user_dp[,user_dp_percentage:=dp_orders/total_orders]
user_dp$dp_orders <- NULL
user_dp$total_orders <- NULL

# pivot
user_dp <- dcast(user_dp, user_id ~ day_part, value.var="user_dp_percentage")

#replace NAs with 0
user_dp[is.na(user_dp)] <- 0

```

### Merging all ordering patterns

```{r}
users_order_patters <- merge(user_orders,user_days,by='user_id')
users_order_patters <- merge(users_order_patters,user_dow,by='user_id')
users_order_patters <- merge(users_order_patters,user_dp,by='user_id')
users_order_patters <- merge(users_order_patters,user_dow_day_part,by='user_id')

#clean the workspace
rm(user_orders,user_days,user_dow,user_dp,user_dow_day_part)
```

# B) Users Product Patterns
## 1) Aisles Percentage of Products

```{r}
user_aisles <- order_products_all[,length(product_id),by=c('user_id','aisle')]
names(user_aisles)[3] <- "prod_per_aisle"
user_products <- order_products_all[,length(product_id),by=c('user_id')]
names(user_products)[2] <- "total_products"

#calculate the percentage
user_aisles <- merge(user_aisles,user_products,by='user_id')
user_aisles <- user_aisles[,user_aisles_percentage:=prod_per_aisle/total_products]
user_aisles$prod_per_aisle <- NULL
user_aisles$total_products <- NULL

# pivot
user_aisles <- dcast(user_aisles, user_id ~ aisle, value.var="user_aisles_percentage")

#replace NAs with 0
user_aisles[is.na(user_aisles)] <- 0

```


## 2) Departments Percentage of Products

```{r}
user_dep <- order_products_all[,length(product_id),by=c('user_id','department')]
names(user_dep)[3] <- "prod_per_dep"

#calculate the percentage
user_dep <- merge(user_dep,user_products,by='user_id')
user_dep <- user_dep[,user_dep_percentage:=prod_per_dep/total_products]
user_dep$prod_per_dep <- NULL
user_dep$total_products <- NULL

# pivot
user_dep <- dcast(user_dep, user_id ~ department, value.var="user_dep_percentage")

#replace NAs with 0
user_dep[is.na(user_dep)] <- 0
```

## 3) Document of Words from Product Descriptions

```{r}
user_words <- order_products_all[,.(user_id,product_id,aisle,department,product_name)]
user_words <- unique(user_words)

# for each user merge the product description into 1 cell
#overall level
user_words_collapsed <- user_words %>% group_by(user_id) %>% summarise(all_words = paste(product_name, collapse=" | "))

#aisle level
user_aisle_words_coll <- user_words %>% group_by(user_id,aisle) %>% summarise(all_words = paste(product_name, collapse=" | "))
user_aisle_words_coll <- dcast(user_aisle_words_coll, user_id ~ aisle, value.var="all_words")
#renaming the columns so that we can distinguish them compared to the percentages
names(user_aisle_words_coll)[2:length(names(user_aisle_words_coll))] <- paste(names(user_aisle_words_coll)[2:length(names(user_aisle_words_coll))],"_w",sep="")


#department level
user_dep_words_coll <- user_words %>% group_by(user_id,department) %>% summarise(all_words = paste(product_name, collapse=" | "))
user_dep_words_coll <- dcast(user_dep_words_coll, user_id ~ department, value.var="all_words")
#renaming the columns so that we can distinguish them compared to the percentages
names(user_dep_words_coll)[2:length(names(user_dep_words_coll))] <- paste(names(user_dep_words_coll)[2:length(names(user_dep_words_coll))],"_w",sep="")
head(user_dep_words_coll)
```

## Merge all the product datasets together

```{r}
user_product_patterns <- merge(user_aisles,user_dep, by='user_id')
user_product_patterns <- merge(user_product_patterns,user_words_collapsed, by='user_id')
user_product_patterns <- merge(user_product_patterns,user_aisle_words_coll, by='user_id')
user_product_patterns <- merge(user_product_patterns,user_dep_words_coll, by='user_id')
```

# Merge the product and the ordering patterns together in one masterfile

```{r}
user_features <- merge(users_order_patters,user_product_patterns,by='user_id')
```


# Save the masterfile but all the individual files separately so that they are easier to work with
```{r}
write.csv(user_features, 'user_features.csv')
write.csv(users_order_patterns, 'users_order_patterns.csv')
write.csv(user_aisles, 'user_aisles.csv')
write.csv(user_dep, 'user_dep.csv')
write.csv(user_words_collapsed, 'user_words_collapsed.csv')
write.csv(user_aisle_words_coll, 'user_aisle_words_coll.csv')
write.csv(user_dep_words_coll, 'user_dep_words_coll.csv')
```

